Comparative Analysis of Approximation Algorithms for Solving The Traveling Salesman Problem

### 2018-04-28 tex/paper.tex

\begin{document}	
	\twocolumn[
	\begin{@twocolumnfalse}
		\author{Mohamed Moanis Ali, Michael Sedrak \\  mohamed.moanis.ali@gmail.com, m.sedrak@live.com}
		\title{Comparative Analysis of Approximation Algorithms for Solving TSP}
		\maketitle
		\begin{abstract}
			The traveling salesman problem is considered one of the hardest problems in computer science with no polynomial runtime algorithm to solve it so far. Nevertheless, TSP is an active research point with more algorithms being developed to either approximately solve the original problem, or to speed it up so larger datasets can be solved. In this work we present a comparative study using four algorithms to solve TSP -genetic algorithm, simulated annealing, nearest neighbor and ant colony optimization to analyze the runtime performance and the correctness of their solution.  The results of the experiments on the Uruguay dataset -using both {Matlab\texttrademark}  and Octave- showed that the nearest neighbor algorithm provided the fastest runtime and a relatively correct solution with $18\%$ from the known optimal solution, while the ant colony optimization proved to be the least correct among the studied algorithms. The study also found a huge performance difference between {Matlab\texttrademark}  and Octave software.
		\end{abstract}

>>>>

\begin{document}	
	\twocolumn[
	\begin{@twocolumnfalse}
		\author{Mohamed Moanis Ali, Michael Sedrak \\  mohamed.moanis.ali@gmail.com, m.sedrak@live.com}
		\title{Comparative Analysis of Approximation Algorithms for Solving The Traveling Salesman Problem}
		\maketitle
		\begin{abstract}
			The traveling salesman problem is considered one of the hardest problems in computer science with no polynomial runtime algorithm to solve it so far. This work presents a comparative study using four approximate algorithms -genetic algorithm, simulated annealing, nearest neighbor and ant colony optimization- to analyze the runtime performance and the correctness of their solution.  The results of the experiments on the Uruguay dataset -using both {Matlab\texttrademark}  and Octave- showed that the nearest neighbor algorithm provided the fastest runtime and a relatively correct solution with $18\%$ from the known optimal solution, while the ant colony optimization proved to be the least correct among the studied algorithms. Also, the simulated annealing algorithm provided the best solution with $11.3\%$ from the optimal. The study also found a huge performance difference between {Matlab\texttrademark}  and Octave software.
		\end{abstract}
